An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-09 paper.tex
Using minted for the listings and source code syntax highlighting.

@@

% This allows Figures to be renamed as Listing, as required by F1000Research.
\usepackage{float}
\newfloat{listing}{thp}{lop}
\floatname{listing}{Listing}

@@

\begin{listing*}
  \begin{verbatim}
    >>> from gaitanalysis.motek import DFlowData
    >>> data = DFlowData('mocap-020.txt', 'record-020.txt', 'meta-020.yml')
    >>> mass = data.meta['subject']['mass']
    >>> data.clean()
    >>> event_df = dflow_data.extract_processed_data(event='Longitudinal Perturbation')
  \end{verbatim}
  \cprotect\caption{Python interpreter session showing how one could load a
    trial into memory, extract the subject's mass from the meta data, run the
    data cleaning process, and finally extract a Pandas \verb|DataFrame|
    containing all of the time histories for a specific event in the trial.}
  \label{lis:dflowdata}
\end{listing*}

@@

\begin{listing*}
  \begin{verbatim}
    >>> from gaitanalysis.gait import GaitData
    >>> gdata = GaitData(event_df)
    >>> gdata.inverse_dynamics_2d(left_markers, right_markers, left_loads,
    ...                           right_loads, mass, 6.0)
    >>> gdata.grf_landmarks('Right Fy', 'Left Fy', threshhold=20.0)
    >>> gdata.split_at('right')
    >>> gdata.plot_gait_cycles('Left Hip Joint Torque', mean=True)
    >>> gdata.save('gait-data.h5')
  \end{verbatim}
  \cprotect\caption{Python interpreter session showing how one could compute
    the inverse dynamics (joint angles and torques), indentify the gait
    landmarks (e.g. heelstrikes), split the data with respect to the gait
    landmarks in a Pandas \verb|Panel|, plot the mean and standard deviation of
    one time history with respect to the gait cycles, and save the data to disk.}
  \label{lis:dflowdata}
\end{listing*}

>>>>

% for nice source code syntax highlighting, also provides Listing env
\usepackage{minted}

@@

@@

\begin{listing*}
  \begin{minted}{python}
    >>> from gaitanalysis.motek import DFlowData
    >>> data = DFlowData('mocap-020.txt', 'record-020.txt', 'meta-020.yml')
    >>> mass = data.meta['subject']['mass']
    >>> data.clean()
    >>> event_df = dflow_data.extract_processed_data(event='Longitudinal Perturbation')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could load a
    trial into memory, extract the subject's mass from the meta data, run the
    data cleaning process, and finally extract a Pandas \verb|DataFrame|
    containing all of the time histories for a specific event in the trial.}
  \label{lis:dflowdata}
\end{listing*}

@@

\begin{listing*}
  \begin{minted}{python}
    >>> from gaitanalysis.gait import GaitData
    >>> gdata = GaitData(event_df)
    >>> gdata.inverse_dynamics_2d(left_markers, right_markers, left_loads,
    ...                           right_loads, mass, 6.0)
    >>> gdata.grf_landmarks('Right Fy', 'Left Fy', threshhold=20.0)
    >>> gdata.split_at('right')
    >>> gdata.plot_gait_cycles('Left Hip Joint Torque', mean=True)
    >>> gdata.save('gait-data.h5')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could compute
    the inverse dynamics (joint angles and torques), indentify the gait
    landmarks (e.g. heelstrikes), split the data with respect to the gait
    landmarks in a Pandas \verb|Panel|, plot the mean and standard deviation of
    one time history with respect to the gait cycles, and save the data to disk.}
  \label{lis:dflowdata}
\end{listing*}
